Association between Breast Cancer and Hepatitis C Virus with Age Confounding

### 2022-11-14 manuscript/manuscript.tex
Update manuscript.tex
update

\title{Proposal: Association between Breast Cancer and Hepatitis C Virus}
\author{Amy Traianou\\
  Department of Statistics\\
  University of Connecticut
}

@@

\paragraph{Introduction}
For this paper I decided to explore the risk factors associated with breast cancer in women. Breast cancer is extremely
prevalent and researchers are constantly trying to determine risk factors to identify women for preventative exams.
There are many studies attempting to determine if there is an association between certain risk factors and 
breast cancer including chronic hepatitis C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.

\paragraph{Specific Aims}
Specifically, I want to determine if there is an association between testing positive for hepatitis C virus
and breast cancer. Both Hepatitis C and breast cancer are extremely prevalent in Egypt \citep{Hussein2021high}. 
Very recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
as a area of interest \citep{arham2022egypt}. Thus, research surrounding these diseases is becoming more
important in the field.

\paragraph{Data}

@@

\begin{tabular}{ | m{5cm} | m{3cm}| m{3cm} | m{2cm} | }
  \hline
  Risk Factor & Study Group & Control & Total\\ 
  \hline
  Anti-HCV Seropositive & 88 & 15 & 103 \\ 
  \hline
  Anti-HCV Seronegative & 317 & 130 & 447 \\ 
  \hline
  Total & 405 & 145 & 550 \\ 
  \hline
\end{tabular}

\paragraph{Research Design and Methods}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8cm]{formula.png}
  \caption{This is the hypergeometric pmf.}
  \label{fig:formula}
\end{figure}

\paragraph{Discussion}

@@

\paragraph{Conclusion}

In conclusion, I propose using data from women in Egypt to determine if there is an association between seropositive Hepatitis C and 
breast cancer. The Egyptian government has identified breast cancer as an area of interest for medical research so it has importance in
the field. Additionally, identifying a new risk factor for breast cancer would increase preventative screening in adult women and hopefully 
improve the ability to discover cancer in earlier stages.

>>>>

\title{Association between Breast Cancer and Hepatitis C Virus with Age Confounding}
\author{Amy Traianou\\
  Department of Statistics\\
  University of Connecticut
}

@@

\begin{abstract}
The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized continuous distribution.
Nevertheless, it has often been misused.

\bigskip
\noindent{\sc Keywords}:
Breslow-Day;
Fisher's Exact Test;
Mantel-Haenszel.
\end{abstract}

\section{Introduction}
\label{sec:intro}

For this paper I decided to explore the risk factors associated with breast cancer in women. Breast cancer is extremely
prevalent and researchers are constantly trying to determine risk factors to identify women for preventative exams.
There are many studies attempting to determine if there is an association between certain risk factors and 
breast cancer including chronic hepatitis C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.

Specifically, I want to determine if there is an association between testing positive for hepatitis C virus
and breast cancer. Both Hepatitis C and breast cancer are extremely prevalent in Egypt \citep{Hussein2021high}. 
Very recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and use each 
other's expertise. The health ministers specifically mentioned research in Hepatitis C and breast cancer
as a area of interest \citep{arham2022egypt}. Thus, research surrounding these diseases is becoming more
important in the field.

\section{Data}
\label{sec:data}

@@

2x2 Contingency Table for all patients.

\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
  \label{table:total}
  \hline
    & HCV Seropositive & HCV Seronegative & Total\\ 
  \hline
  Breast Cancer & 88 & 317 & 405 \\ 
  \hline
  No Cancer Diagnosis & 15 & 130 & 145 \\ 
  \hline
  Total & 103 & 447 & 550 \\ 
  \hline
\end{tabular}

2x2 Contingency Table for pateints younger than 45.

\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
  \label{table:young}
  \hline
    & HCV Seropositive & HCV Seronegative & Total\\ 
  \hline
  Breast Cancer & 17 & 110 & 127 \\ 
  \hline
  No Cancer Diagnosis & 2 & 91 & 93 \\ 
  \hline
  Total & 19 & 201 & 220 \\ 
  \hline
\end{tabular}

2x2 Contingency Table for patients older than 45.

\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
  \label{table:old}
  \hline
    & HCV Seropositive & HCV Seronegative & Total\\ 
  \hline
  Breast Cancer & 71 & 207 & 278 \\ 
  \hline
  No Cancer Diagnosis & 13 & 39 & 52 \\ 
  \hline
  Total & 84 & 246 & 330 \\ 
  \hline
\end{tabular}

\section{Methods}
\label{sec:methods}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8cm]{formula.png}
  \caption{Hypergeometric pmf.}
  \label{fig:formula}
\end{figure}

\section{Application}
\label{sec:app}

@@

\section{Discussion}
\label{sec:discuss}
